---
title: Data Transformation Part 3 Minilab
author: all participating group member names here
date: today
format: 
    gfm: 
      toc: true
      toc-depth: 2
      fig-height: 4
      fig-width: 9
editor: visual
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)

```

# Introduction

This investigation gives you practice with data transformation and data visualization R procedures from Chapters 1 and 3. You will use **the flights** data set from the nycflights package.

# Questions

1.  Which three carriers have the worst average arrival delays? Your script should just print the top 3 carrier codes and their associated delays.

**Answer:**

```{r}

```

2.  Create a scatterplot (Hint: `geom_point()`) of average departure delay by month for three major airlines American, Delta and United. You can use the **airlines** data set to find the carrier code for these airlines. Your plot should use a different color for each airline. In which three months do delays tend to be longest?

**Answer:**

```{r}

```

3.  How do delays vary over the course of the day? Illustrate your answer with a plot. (Hint: Consider hourly averages.)

```{r}

```
